### 2012-11-13 doc/progress_plan/report.tex
Started adding other sections to document

Since the advent of the 'Digital Age' and the ability of computers to copy and
reproduce information for a negligible cost, the amount of information
available to researchers has been increasing drastically.  A 2009 study by B-C
Bj\"{o}rk suggests that approximately 1.4 Million papers were published in the
year 2006 alone\cite{bjork2009}. Moreover, the growing popularity of Open Access
publishing (making papers available for free online\cite{Suber2012}) across
most scientific disciplines\cite{bjork2009}\cite{harnad2004comparing} is
providing researchers with an even larger volume of information to be
processed. As available information increases, relevant material becomes
progressively more difficult to find and the need for an automated information
retrieval tool more apparent.

Partridge aims to autonomously process as many scientific papers as possible to
facilitate researchers who would otherwise be required to manually read each
paper themselves. This should reduce the amount of information that the reader
is required to process themselves, thereby speeding up the research process.
Partridge will achieve this through the use of several existing techniques in
the field of Natural Language Processing which are discussed below.

@@

There are already several tools that help researchers manage the vast library
of internet journals available on the internet. Search engines such as Google
({\url{http://www.google.com/}}), and social citation management tools such as
CiteULike ({\url{http://www.citeulike.org}}), do offer some assistance in
tracking down relevant information. However, these tools are often too general
or rely upon the user knowing exactly what keywords to search for before
carrying out the search. These drawbacks are further discussed in Section
\ref{sec:prior_art} below.

To overcome the drawbacks of these existing systems, Partridge will make use of
several modern Natural Language Processing (NLP) techniques.  NLP enables the
automated extraction of meaningful information from texts written in human
languages such as English or French. There have already been several papers on
using NLP for detecting emotions in suicide notes\cite{citeulike:11077287}, the
genre of a web page on the World Wide Web\cite{citeulike:11288938} and
emotional polarity of a phrase or sentence\cite{Wilson05Polarity}. Liakata et
al. have also used NLP techniques to classify sentences within scientific
papers to determine what scientific concept they relate to (i.e. does this
sentence cover background information or is it a part of the
hypothesis?)\cite{citeulike:10444769}. Partridge will build upon and make use
of these existing applications of NLP to filter and retrieve data from
scientific papers in a novel way.

@@

\subsection{Literature Review}
Natural Language Processing is still a relatively unexplored discipline and as
such is still a very active area of research and development within the
Artificial Intelligence community. E. Liddy defines Natural Language Processing as:

\begin{quotation} 
A theoretically motivated range of computational techniques for analyzing and
representing naturally occurring texts at one or more levels of linguistic
analysis for the purpose of achieving human-like language processing for a
range of tasks or applications. \cite{liddy2001natural} 
\end{quotation}

@@

It is therefore necessary to define what a 'human-like way' of processing
scientific papers on the internet consists of. Steven Krug is an expert in the field of
human-computer interaction on the internet. In `Don't Make Me Think', Krug
suggests that when browsing the internet, humans find it much easier to locate
specific information within a labelled and logically structured document than
one that is provided as a single text entity.\cite{Krug:2005:DMM:1051204}. In
order to help humans to find relevant research papers, Partridge will represent
all research papers in its repository in a logical hierarchy that can be
queried directly by the human users and also processed using other NLP
techniques to extract further information.

Partridge's document storage format should therefore be formalised to provide a
standard way of processing each document. In their 2007 paper, Soldatova and
Liakata propose a methodology for storing the Core Information about Scientific
Papers (CISP) as a way to formally represent scientific concepts that should be
present in the papers in a logical ontology\cite{soldatova2007ontology}. They
then proceed to define a schema for their CISP ontology that defines the
Core Scientific Concepts (CoreSC) as part of the XML document
itself\cite{liakata2008guidelines}. Using this format for Partridge would allow
the system to read and process the ART corpus produced using CoreSC markup

@@

Search engines are helpful in locating pages and websites within the World Wide
Web. Unfortunately, the problem space they deal with is usually too big for
them to find scientific papers and journals given a set of keywords. Internet
search engines index a huge proportion of irrelevant information compared to
useful information\cite{Berghel1997}, and as a result, even relatively specific
queries such as effects of gravity on rockets" yield millions of results (as
shown in Figure \ref{fig:rocket_results}).

@@

>>>>

Since the advent of the 'Digital Age' and the ability of computers to copy and
reproduce information for a negligible cost, the amount of information
available to researchers has been increasing drastically.  B-C Bj\"{o}rk (2009)
estimates that approximately 1.4 Million papers were published in the year 2006
alone\cite{bjork2009}. Moreover, the growing popularity of Open Access
publishing (making papers available for free online\cite{Suber2012}) across
most scientific disciplines\cite{bjork2009}\cite{harnad2004comparing} is
providing researchers with an even larger volume of information to be
processed. As available information increases, relevant material becomes
progressively more difficult to find and the need for an automated information
retrieval tool more apparent. The problem is even more vital for General
Practitioners. Goldacre (2008:97) points out that ``there have been an
estimated 15 million medical academic articles published so far, and 5000
journals published every month... picking out what's relevant is a garganutan
task."\cite{goldacre2009bad}

Partridge aims to autonomously process as many scientific papers as possible to
facilitate researchers who would otherwise be required to manually read each
paper themselves. This should reduce the amount of information that the reader
is required to process themselves, thereby speeding up the research process.
Partridge will achieve this through the use of several existing techniques in
Natural Language Processing which are discussed below.

@@

There are already several tools that help researchers manage the vast library
of journals available on the internet. Search engines such as Google
({\url{http://www.google.com/}}), and social citation management tools such as
CiteULike ({\url{http://www.citeulike.org}}), do offer some assistance in
tracking down relevant information. However, these tools are often too general
or rely upon the user knowing exactly what keywords to use before carrying out
the search. These drawbacks are further discussed in Section
\ref{sec:prior_art} below.

To overcome the drawbacks of these existing systems, Partridge will make use of
several cutting edge Artificial Intelligence (AI) techniques in order to analyse and
process the papers in a more in depth way. AI is a very complex and field and
implementing the above features will be incredibly challenging. To help with
this, Partridge will build upon the system implemented by Liakata et al. for
classifying papers on a sentence-by-sentence basis\cite{citeulike:10444769} and
make use of Natural Language Toolkit for Python
\cite{Bird:2006:NNL:1225403.1225421}

@@

\subsection{Literature Review}

\subsubsection{Natural Language Processing}

Start with history of NLP.

Natural Language Processing is
still a relatively unexplored discipline and as such is still a very active
area of research and development within the Artificial Intelligence
community\cite{liddy2001natural}. Liddy goes on to define Natural Language
Processing as:

\begin{quotation} 
A theoretically motivated range of computational techniques for analyzing and
representing naturally occurring texts at one or more levels of linguistic
analysis for the purpose of achieving human-like language processing for a
range of tasks or applications \it{(Ibid)}.  
\end{quotation}

@@

It is therefore necessary to define what a 'human-like way' of processing
scientific papers.  Krug (2005), suggests that when browsing the internet,
humans find it much easier to locate specific information within a labelled and
logically structured document than one that is provided as a single text
entity\cite{Krug:2005:DMM:1051204}. In order to help humans to find relevant
research papers, Partridge will represent all research papers in its repository
in a logical hierarchy that can be queried directly by the human users and also
processed using other NLP techniques to extract further information.
Partridge's document storage format should therefore be standardised to provide
a uniform way of processing each document.

\subsubsection{CISP, CoreSC and SAPIENTA}

Soldatova and Liakata(2007) proposed a methodology for storing the Core
Information about Scientific Papers (CISP) as a way to formally represent
scientific concepts that should be present in the articles in a logical
ontology\cite{soldatova2007ontology}. They then proceed to define a schema for
their CISP ontology that defines the Core Scientific Concepts (CoreSC) as part
of the XML document itself\cite{liakata2008guidelines}.

Partridge will make use of
several modern Natural Language Processing (NLP) techniques.  NLP enables the
automated extraction of meaningful information from texts written in human
languages such as English or French. There have already been several papers on
using NLP for detecting emotions in suicide notes\cite{citeulike:11077287}, the
genre of a web page on the World Wide Web\cite{citeulike:11288938} and
emotional polarity of a phrase or sentence\cite{Wilson05Polarity}. Liakata et
al. have also used NLP techniques to classify sentences within scientific
papers to determine what scientific concept they relate to (i.e. does this
sentence cover background information or is it a part of the
hypothesis?). Partridge will build upon and make use
of these existing applications of NLP to filter and retrieve data from
scientific papers in a novel way.

@@

Search engines are helpful in locating pages and websites within the World Wide
Web. Unfortunately, the problem space they deal with is usually too big for
them to find scientific papers and journals given a set of keywords. Internet
search engines index a huge proportion of irrelevant information compared to
useful information\cite{Berghel1997}, and as a result, even relatively specific
queries such as ``effects of gravity on rockets" yield millions of results (as
shown in Figure \ref{fig:rocket_results}).

@@

\subsection{Methodology}

\subsection{Prototyping/Pilot Studies}

\subsection{Subsequent Changes to Methodology}
